Analysis of Cartesian Genetic Programming's Evolutionary Mechanisms

### 2013-05-23 CGP Journal/main.tex
More fill in, more citations

TODO Previous work on understanding evolution, especially CGP.

@@

@@

\section{Duplicate Evaluation Avoidance}
\label{sec:duplicate}
CGP's mutation operator is traditionally applied to all genes equally, with no
consideration if genes are part of an active or inactive node.  This has the
potential to lead offspring who's only mutated genes are part of inactive nodes.
These offspring are actively identical (contain identical active genes) to their
parents, and therefore by definition have identical fitness to their parents.
As such, evaluating these individuals is wasteful, as their fitness can be
assigned without the computational complexity of performing an evaluation.
Previous work~\cite{goldman:2013:cgpwaste} has taken an initial look at the
effect this waste can have, and proposed \emph{Skip}, \emph{Accumulate}, and
\emph{Single} as methods for avoiding or preventing these duplicate evaluations.

TODO Explain that inactive / active is knowable before evaluation.

@@

TODO Consider adding 5-bit Parity or Equality, 11-bit Multiplexer.

>>>>

@@

There have been a number of previous studies into various aspects of GP evolution.
For instance~\cite{daida3:2003:treebias} looked into how trees of specific shapes,
which helped inspire the use of new grammar based operations~\cite{xuan:2006:grammar}.
Analysis of the root cause of bloat has helped to inform methods for controlling
bloat~\cite{luke:2006:bloat}.  A few studies of evolutionary mechanisms have also
been done in CGP directly, related to bloat~\cite{miller:2001:bloat},
neutrality~\cite{vassilev:2000:neutrality}, and structural bias~\cite{payne:2009:bias}.

@@

\section{Duplicate Evaluation Avoidance}
\label{sec:duplicate}
CGP's mutation operator is traditionally applied to all genes equally, with no
consideration if genes are part of an active or inactive node.  This has the
potential to lead offspring who's only mutated genes are part of inactive nodes.
These offspring are actively identical (contain identical active genes) to their
parents, and therefore by definition have identical fitness to their parents.
As such, evaluating these individuals is wasteful, as their fitness can be
assigned without the computational complexity of performing an evaluation.
Furthermore, calculating which nodes are active before evaluating an individual
improves evaluation speed~\cite{vasicek:2012:efficient}, meaning detecting when duplicated individuals are
created can be done without significant computational overhead.
Previous work~\cite{goldman:2013:cgpwaste} has taken an initial look at the
effect this waste can have, and proposed \emph{Skip}, \emph{Accumulate}, and
\emph{Single} as methods for avoiding or preventing these duplicate evaluations.

@@

%TODO Consider adding 5-bit Parity or Equality, 11-bit Multiplexer.
